Shared Characterizations of Demands and Resources across O*NET Job Elements

### 2025-06-12 Submission.Rmd
pushing to laptop for Dunn brothers

abstract: |
  Many discussions of job demands and resources include a tacit characterization that job elements are either resources or demands. This study documents variability in ratings of O\*Net job characteristics with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes. We additionally explore the potential moderating role of resources on these relationships. The results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, challenging elements tend to also be experienced as job resources. Furthermore, greater experienced resources moderated the challenge-engagement relationship as well as the hindrance-stress and hindrance-burnout relationships. These findings broadly suggest that challenging demands may also provide opportunity in the form of job resources, and what is viewed as a *hindrance* exhibits considerable variability. These findings have implications for job design and management particularly with regard to opportunity with *some* demanding elements: these may be candidates for growth opportunity.

@@

csl               : "apa7.csl"
documentclass     : "apa7" #interact
classoption       : "man"
output:
  papaja::apa6_pdf:
    latex_engine: xelatex 
---

@@

@@

The final usable sample consisted of `r nrow(data)`. Regarding tenure, `r round(a[1,3],2)`% had been in their referent job less than 6 months, `r round(a[2,3],1)`% between 6 months and a year, `r round(a[3,3],2)`% between one and five years, `r round(a[4,3],2)`% between 5 and 10 years, and `r round(a[5,3],2)`% more than 10 years. Respondent ages ranged from 18 to 65 with an average of `r round(mean(data[,403], na.rm=TRUE),2)` years old (*SD* = `r round(sd(data[,403], na.rm=TRUE),2)`). The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (`r round(b[2,3],2)`%) or male (`r round(b[5,3],2)`%).

>>>>

abstract: |
  Discussions of job characteristics often include a (tacit) characterization that these job elements are either resources or demands. The current study documents variability in ratings of O\*Net specifications with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes. We additionally explore the potential moderating role of resources on these relationships. Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, challenging elements tend to *also* be interpreted as job resources. Furthermore, greater experienced resources moderate the challenge--engagement relationship as well as the hindrance-stress and hindrance--burnout relationships. These findings broadly suggest that challenging demands may also provide opportunity in the form of job resources, and what is viewed as a *hindrance* exhibits considerable variability.

@@

csl               : "sage-harvard.csl"
documentclass     : "apa7" #interact
classoption       : "man"
output:
  papaja::apa6_pdf:
    latex_engine: xelatex 
---

@@

8,000 words inclusive of everything, references, etc

Abstract = 150 words

preference for Word document

@@

The Montclair State University Institutional Review Board approved the project and respondents provided consent after reviewing a project description but before starting the survey. Written consent was obtained via The final screened sample consisted of `r nrow(data)`. Regarding tenure, `r round(a[1,3],2)`% had been in their referent job less than 6 months, `r round(a[2,3],1)`% between 6 months and a year, `r round(a[3,3],2)`% between one and five years, `r round(a[4,3],2)`% between 5 and 10 years, and `r round(a[5,3],2)`% more than 10 years. Respondent ages ranged from 18 to 65 with an average of `r round(mean(data[,403], na.rm=TRUE),2)` years old (*SD* = `r round(sd(data[,403], na.rm=TRUE),2)`). The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (`r round(b[2,3],2)`%) or male (`r round(b[5,3],2)`%).
